Global patterns of forest autotrophic carbon fluxes

### 2020-02-25 manuscript/manuscript draft.Rmd
Update manuscript draft.Rmd

Our analysis clarifies how FACF vary with latitude and climate on a global scale, with some important implications for how forest carbon cycling relates to climate and, by extension, how it is likely to respond to climatic warming. We find no support for non-linear trends in mature forest C cycling with respect to latitude or $MAT$, and no distinct trends in C allocation across the global scale (Fig. 2). The implication is that under warmer conditions with similar moisture availability--and within the temperature range to which forest communities are adapated and acclimatized--higher temperatures result in a generalized acceleration of FACF, with no major shifts in C allocation among subsidiary fluxes. This is consistent with observations of continental- to global-scale increases in $GPP$ (*[Li & Xiao 2019](https://www.mdpi.com/2072-4292/11/21/2563)*), $ANPP_{woody stem}$ (*[Brienen et al., 2015](https://www-nature-com.smithsonian.idm.oclc.org/articles/nature14283)*), as well as some C cycle components not considered here--tree mortality (*[Brienen et al., 2015](https://www-nature-com.smithsonian.idm.oclc.org/articles/nature14283)*; **some McDowell Ref-KAT**), soil respiration ([Bond Lamberty & Thompson 2010](https://www-nature-com.smithsonian.idm.oclc.org/articles/nature08930/)), heterotrophic soil respiration ([Bond-Lamberty et al. 2018](https://www-nature-com.smithsonian.idm.oclc.org/articles/s41586-018-0358-x)). Of course, other factors such as rising CO~2~ are also at play... Of course, actual climatic changes will result in very different sets of conditions than represented across geographic gradients in climate, but our analysis clarifies how carbon cycles through contemporary forest ecosystems. As we enter a period of accelerating climatic change, understanding of the fundamental climatic controls on FACF sets a foundation for understanding patterns of change. **[work on this]**

>>>>

Our analysis clarifies how FACF vary with latitude and climate on a global scale, with some important implications for how forest carbon cycling relates to climate and, by extension, how it is likely to respond to climatic warming. We find no support for non-linear trends in mature forest C cycling with respect to latitude or $MAT$, and no distinct trends in C allocation across the global scale (Fig. 2). The implication is that under warmer conditions with similar moisture availability--and within the temperature range to which forest communities are adapated and acclimatized--higher temperatures result in a generalized acceleration of FACF, with no major shifts in C allocation among subsidiary fluxes. This is consistent with observations of continental- to global-scale increases in $GPP$ (*[Li & Xiao 2019](https://www.mdpi.com/2072-4292/11/21/2563)*), $ANPP_{woody stem}$ (*[Brienen et al., 2015](https://www-nature-com.smithsonian.idm.oclc.org/articles/nature14283)*), as well as some C cycle components not considered here--tree mortality (*[Brienen et al., 2015](https://www-nature-com.smithsonian.idm.oclc.org/articles/nature14283)*; **some McDowell Ref-KAT**), soil respiration ([Bond Lamberty & Thompson 2010](https://www-nature-com.smithsonian.idm.oclc.org/articles/nature08930/)), heterotrophic soil respiration ([Bond-Lamberty et al. 2018](https://www-nature-com.smithsonian.idm.oclc.org/articles/s41586-018-0358-x)). Of course, other factors such as rising CO~2~ are also at play, and such increases are not universal (e.g., [Rutishauser et al., 2019](https://onlinelibrary-wiley-com.smithsonian.idm.oclc.org/doi/full/10.1111/gcb.14833?casa_token=imtB9LD9mL8AAAAA%3AYWgsqNUfRkgs6_dIuDzmwUzL0qVyyxojhbj3jjfRcykBy8ay9T4qMOKPeOPytSGET9muIs8myhQOh3E))... Of course, actual climatic changes will result in very different sets of conditions than represented across geographic gradients in climate, but our analysis clarifies how carbon cycles through contemporary forest ecosystems. As we enter a period of accelerating climatic change, understanding of the fundamental climatic controls on FACF sets a foundation for understanding patterns of change. **[work on this]**
